Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-14 docs/ms.tex
Update ms.tex

\begin{keywords}
  gravitational lensing
\end{keywords}

@@

As described in section 3.1, we use the mean of posterior samples as the most probable $g_{i}$ and 
the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
most-likely value and uncertainty of m and c.

Due to the limitation of galaxy number we are not able to get an exact value for m and c. However in our result 
both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
relatively large uncertainty, it is only an rough estimate of bias level.
\begin{figure}
\includegraphics[scale=0.5]{fig/g1bias}

@@

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error 
affects the variance and bias of shear inference.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation (7).
However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
\begin{figure}
\includegraphics[scale=0.48]{fig/errorN8}
\caption{Figure 5 shows how the mean square error of sample mean estimate varies with the number of patches used, while shape measurement error is considered as described in Section 3.4 .
The horizontal line denotes the mean square of mean ellipticity estiimator which does not depend on number of patches. }
\end{figure}

>>>>

\begin{keywords}
  gravitational lensing ; hierarchical Bayesian inference
\end{keywords}

@@

As described in section 3.1, we use the mean of posterior samples as the most probable $g_{i}$ and 
the standard deviation as uncertainty. A weighted minimum $\chi^{2}$ linear fit is performed to get the
most-likely value and uncertainty of m and c. for $g_{1}$ component we get $m=-6.09\times10^{-4}\pm2.39\times10^{-3}$
and $c=(1.82\pm1.44)\times10^{-4}$, while for $g_{2}$ component
we have $m=-3.48\times10^{-4}\pm2.14\times10^{-3}$ and $c=(2.01\pm1.29)\times10^{-4}$.
Due to the limitation of galaxy number we are not able to get an exact value for m and c. However in our result 
both the most-like and uncertainty of m are around $10^{-3}$ and for c they are around $10^{-4}$ . Due to the
relatively large uncertainty, it is only an rough estimate of bias level.
\begin{figure}
\includegraphics[scale=0.5]{fig/g1bias}

@@

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error 
affects the variance and bias of shear inference.
In principle, if the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$
is known the likelihood $p(\epsilon_{ob}|g,\alpha)$ can be calculated using the convolution as equation (7).
However, due to the limitation of computational time we avoid to do this convolution but use $\epsilon_{ob}$
as an estimator of $\epsilon_{\ell}$.
The likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})$ we use in the simulation is a 2D
Gaussian with mean equals $\epsilon_{\ell}$ and $\sigma$ equals 0.05 .
Figure 5 shows the mean square error of the sample mean estimates in comparison with mean ellipticity estimator.
\begin{figure}
\includegraphics[scale=0.48]{fig/errorN8}
\caption{Figure 5 shows how the mean square error of sample mean estimate varies with the number of patches used, while shape measurement error is considered as described in Section 3.4 .
The horizontal line denotes the mean square of mean ellipticity estiimator which does not depend on number of patches. }
\end{figure}
We can see that our proposed method still works well under shape measurement error, even when we do not have the exact likelihood
of true lensed ellipticity. It means that this hierarchical Bayesian method does not only naturally cope with model fitting shape measurement 
method but is also compatible with ellipticity point estimators.
